TIM: Tree Imaging Machine for low-cost digital images of tree cores and cookies

### 2025-04-04 docs/writing/paper.tex
Adding some context to the introduction of automatic tree ring detection

% Sandy got back to me! :)
We tested a scanned cookie of size (HEIGHT)X(WIDTH) (WAITING FOR SANDY) pixels from TIM with the R-CNN presented by \citeauthor{polacek_automation_2023} on two servers. The first being the high-performance UBC ARC Sockeye which completed the task in 15 minutes. As many do not have access to such powerful computing, we also tested
the same image on an RTX A6000 GPU server---taking 3.5 hours to complete the task for approximately \$3.50 USD. 
While the results of automated tree rings are promising, further testing is necessary to test the feasibility of running this model on an edge computer or developing integrations for TIM with a remote server.

>>>>

% Sandy got back to me! :)
In it's current state, TIM only provides scanned images and requires users to import them into other tools to measure tree-ring widths or count vessels.
A great addition to TIM would be to use computer vision models to automatically detect tree-ring widths or other metrics while capturing images.  
We tested a scanned cookie of size (HEIGHT)X(WIDTH) (WAITING FOR SANDY) pixels from TIM with the R-CNN presented by \citeauthor{polacek_automation_2023} on two servers. The first being the high-performance UBC ARC Sockeye which completed the task in 15 minutes. 
As many do not have access to such powerful computing, we also tested the same image on an RTX A6000 GPU server---taking 3.5 hours to complete the task for approximately \$3.50 USD. 
Although the Jetson is not as powerful as these servers, running these models in parallel to the image capturing algorithms could be a great extension to further reduce manual data annotation of tree-rings.
Further development would be required to run the deep learning models on the Jetson itself or with a web server to offload the heavier computation.
